Explainability and Adversarial Robustness for RNNs

### 2020-02-19 paper/paper.tex
Add IEEE copyright notice

\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[pdfauthor={Alexander Hartl, Maximilian Bachl, Joachim Fabini, Tanja Zseby},
pdftitle={Explainability and Adversarial Robustness for RNNs}]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{subfig}

@@

\maketitle%

@@

\begin{figure}
\includegraphics[width=\columnwidth]{{"../plots/plot_pdp/flows_pdp_outcomes_0_3.pickle_10_Normal"}.pdf}
\caption{PD plot for the source and destination port features.}
\label{fig:pdps}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage[inline]{enumitem}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[pdfauthor={Alexander Hartl, Maximilian Bachl, Joachim Fabini, Tanja Zseby},
pdftitle={Explainability and Adversarial Robustness for RNNs}]{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[numbers]{natbib}
\usepackage{subfig}
\usepackage{tikz}

@@

\newcommand\copyrighttext{%
  \footnotesize \textcopyright 2020 IEEE. Personal use of this material is permitted.
  Permission from IEEE must be obtained for all other uses, in any current or future
  media, including reprinting/republishing this material for advertising or promotional
  purposes, creating new collective works, for resale or redistribution to servers or
  lists, or reuse of any copyrighted component of this work in other works.}
\newcommand\copyrightnotice{%
\begin{tikzpicture}[remember picture,overlay]
\node[anchor=south,yshift=10pt] at (current page.south) {\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\copyrighttext}}};
\end{tikzpicture}%
}

\maketitle%
\copyrightnotice

@@

\begin{figure}
\includegraphics[width=\columnwidth]{{"plots/plot_pdp/flows_pdp_outcomes_0_3.pickle_10_Normal"}.pdf}
\caption{PD plot for the source and destination port features.}
\label{fig:pdps}
\end{figure}
